A Study on Common Bug Fix Patterns in Rust

### 2022-10-16 sections/methodology.tex
applied fixes

    \node (codeA) [fill=yellow!20, rounded corners=1ex] at (10, 0) {%
    \centering
    \begin{minipage}{10cm}
    \centering
    \begin{lstlisting}[language=Rust, style=colouredRust]
      fn sample() {
        // ...
        -- let receiver = foo(arg1, tail, head)
        ++ let receiver = foo(arg1, &tail, head.clone())
        // ...
      }
    \end{lstlisting}

    \end{minipage}%
    };

@@

\begin{table}
\caption{\label{table:repos} Target repositories for mining}
\begin{tabular}{l r r r r}
    Project Name & Stars(k) & LOC & \# Commits & Avg. Code Churn \\
    denoland/deno & 84.7 & 562468 & 7730 & 49.22 \\
    tauri-apps/tauri & 48.5 & 130726 & 2929 & 31.67 \\
    alacritty/alacritty & 41.2 & 45803 & 2017 & 27.53 \\
    sharkdp/bat & 36.4 & 93258 & 2392 & 59.13 \\
    starship/starship & 28 & 176630 & 2290 & 25.1 \\
    rust-lang/rustlings & 28.7 & 9852 & 1391 & 8.92 \\
    meilisearch/meilisearch & 28.6 & 66872 & 3849 & 279.7 \\
    sharkdp/fd & 24.2 & 10383 & 1025 & 12.2 \\
    swc-project/swc & 23.5 & 13512766 & 5205 & 44.34 \\
    yewstack/yew & 23.2 & 112972 & 2239 & 21.79 \\
    xi-editor/xi-editor & 19.5 & 58783 & 2104 & 28.67 \\
    AppFlowy-IO/AppFlowy & 25.9 & 182830 & 2600 & 29.49 \\
    firecracker-microvm/firecracker & 18.9 & 156759 & 3536 & 58.26 \\
    nushell/nushell & 20.3 & 181710 & 5922 & 22.38 \\
    ogham/exa & 18.9 & 17114 & 1558 & 11.99 \\
    SergioBenitez/Rocket & 18.2 & 90055 & 2127 & 19.75 \\
    rustdesk/rustdesk & 27.7 & 85322 & 1664 & 72.81 \\
    tokio-rs/tokio & 17.2 & 126089 & 3006 & 28.87 
\end{tabular}
\end{table}

>>>>

    \node (codeA) [fill=yellow!20, rounded corners=1ex] at (10, 0) {%
    \centering
    \begin{minipage}{10cm}
    \centering
    \begin{lstlisting}[language=Rust, style=colouredRust]
      fn sample() {
        // ...
        -- let receiver = foo(arg1, tail, head)
        ++ let receiver = foo(arg1, &tail, head.clone())
        // ...
      }
    \end{lstlisting}
    \end{minipage}%
    };

@@

\begin{table}
\caption{\label{table:repos} Target repositories for mining}
\begin{tabular}{l r r r r}
    Project Name & Stars(k) & LOC & \# Commits & Avg. Code Churn \\
    denoland/deno & 84.7 & 146055 & 7730 & 49.22 \\
    tauri-apps/tauri & 48.5 & 50014 & 2929 & 31.67 \\
    alacritty/alacritty & 41.2 & 30124 & 2017 & 27.53 \\
    sharkdp/bat & 36.4 & 9496 & 2392 & 59.13 \\
    starship/starship & 28 & 34888 & 2290 & 25.1 \\
    rust-lang/rustlings & 28.7 & 5067 & 1391 & 8.92 \\
    meilisearch/meilisearch & 28.6 & 25981 & 3849 & 279.7 \\
    sharkdp/fd & 24.2 & 6542 & 1025 & 12.2 \\
    swc-project/swc & 23.5 & 346501 & 5205 & 44.34 \\
    yewstack/yew & 23.2 & 44295 & 2239 & 21.79 \\
    xi-editor/xi-editor & 19.5 & 39292 & 2104 & 28.67 \\
    AppFlowy-IO/AppFlowy & 25.9 & 57646 & 2600 & 29.49 \\
    firecracker-microvm/firecracker & 18.9 & 82021 & 3536 & 58.26 \\
    nushell/nushell & 20.3 & 163562 & 5922 & 22.38 \\
    ogham/exa & 18.9 & 10852 & 1558 & 11.99 \\
    SergioBenitez/Rocket & 18.2 & 68952 & 2127 & 19.75 \\
    rustdesk/rustdesk & 27.7 & 48115 & 1664 & 72.81 \\
    tokio-rs/tokio & 17.2 & 121400 & 3006 & 28.87 
\end{tabular}
\end{table}

### 2022-10-16 sections/results.tex
applied fixes

\textbf{RQ1. Does our data modelling approach capture the most important aspect of program changes?}

@@

{\bf There is no text in this subsection.}

@@

>>>>

\textbf{Does our data modelling approach capture the most important aspect of program changes?}

@@

\textbf{What are the general fix patterns in Rust, and how often do they apply?}

We collected 60583 datapoints for general fix patterns using a server with Xeon Gold 5120 Processor (Q3-2017, 14-core 2.2 to 3.2GHz) and the data collection took around 26 hours to complete for both $D_g$ and $D_b$. We used $\epsilon=0.0001$ and $Z=5$ as our DBSCAN parameters and that resulted in 577 clusters. After manual analysis as described in~\ref{sec:manual_analysis_cluster_selection} we ended up with 10 general patterns which we introduce here:

@@

\textbf{What are borrow-checker related fix patterns in Rust, and how often do they apply?}

We collected 27143 datapoints for borrow-checker related fix patterns. We used $\epsilon=0.001$ and $Z=5$ as our DBSCAN parameters and that resulted in 102 clusters. After manual analysis as described in~\ref{sec:manual_analysis_cluster_selection} we ended up with 9 borrow-checker related fix patterns which we introduce here:
